---
title: "MSD 2019 Final Project"
subtitle: "A replication and extension of Chilling Effects: Online Surveillance and Wikipedia Use by Jonathon W. Penney, Berkeley Technology Law Journal"
author: "Thanaspakorn Niyomkarn, Alex Li Kong, and Sang Won Lee (tn2381, alk2225, and sl4447)"
date: '`r Sys.time()`'
output:
  pdf_document:
    toc: yes
    toc_depth: 3
---

# 1. Introduction

This Rmd file attempts to replicate and extend the results in Chilling Effects: Online Surveillance and Wikipedia Use by Jonathon W. Penney in Berkeley Technology Law Journal. The author is a research fellow at University of Toronto. This single author paper has H5-index of 21. This paper is about the NSA/PRISM surveillance 2007, where United States National Security Agency (NSA) started collecting Internet communications from various US Internet companies. This information was made public in 2013 by Edward Snowden revelations. This paper deals with the NSA paranoia where the paper studies traffic to Wikipedia articles on topics that raise privacy concerns for Wikipedia users before and after the Edward Snowden revelations. The Wikipedia traffic was chosen because over 50% of Internet users use Wikipedia as a source of information. Over 1/3 of Americans annually access Wikipedia as a source of information and is in top 10 of most popular sites on the internet.



```{r setup, include=FALSE}
library(scales)
library(tidyverse)
library(lubridate)
library(wikipediatrend)

theme_set(theme_bw())

knitr::opts_chunk$set(echo = TRUE)
```

# 2. Reproducing the Original Study

```{r load data}
load("data/terrorism_data.RData")
load("data/infra_data.RData")
load("data/popular_data.RData")
```



## 2.1 Total views of terrorism-related keywords before and after the incident

```{r}
terrorism_data %>%
  mutate(before_after = ifelse(date < '2013-06-01', "Before_June_2013", "After_June_2013")) %>%
  group_by(before_after) %>%
  summarise(total_views = sum(views)) %>%
  ggplot(aes(x= factor(before_after, level = c("Before_June_2013", "After_June_2013")), y=total_views, width=0.5)) +
  scale_y_continuous(name="Total Views", labels = comma) +
  xlab("Time") +
  geom_text(aes(label=comma(total_views)), vjust=-0.3, color="black", size=3.5) +
  theme_bw(base_size = 10) +
  geom_bar(stat="identity") +
  ggtitle("Total views of terrorism-related keywords before and after the incident")
```

## 2.2 Linear model with interactions: Analysis and Plots

```{r }
lm_plot_topic <- function(input_df, gg_title){

df <- data.frame(input_df)
df <- df %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views))
df$surveillence <- 'before'
df$surveillence[df$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = df)
print(summary(model))


df$prediction <- predict(model, df)
df$se <- predict(model, df,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
df$LoCI <- df$prediction - z.val * df$se
df$HiCI <- df$prediction + z.val * df$se

df$month <- ymd(df$month)

ggplot(df,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = df, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma) +
  ggtitle(gg_title)
}
```


```{r}
lm_plot_topic(terrorism_data, 'Terrorism-related keywords trend before and after June 2013')
```

```{r}
lm_plot_topic(popular_data, 'Popular keywords trend before and after June 2013')
```

```{r}
lm_plot_topic(infra_data, 'Infrastructure security-related keywords trend before and after June 2013')
```

# 3. Extended Analysis

## 3.1 Longer Trend Analysis

## 3.2 Per-keyword Analysis

```{r}
lm_plot_keyword <- function(input_df, article_name, gg_title){

df <- data.frame(input_df)
df <- df %>% 
  group_by(article ,month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) %>%
  filter(article == article_name)  

df$surveillence <- 'before'
df$surveillence[df$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = df)
print(summary(model))


df$prediction <- predict(model, df)
df$se <- predict(model, df,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
df$LoCI <- df$prediction - z.val * df$se
df$HiCI <- df$prediction + z.val * df$se

df$month <- ymd(df$month)

ggplot(df,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = df, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma) +
  ggtitle(gg_title)
}
```

```{r}
lm_plot_keyword(terrorism_data, 'al-qaeda', 'Trend for \'al-qaeda\' before and after June 2013')
```

```{r}
lm_plot_keyword(terrorism_data, 'terror', 'Trend for \'terror\' before and after June 2013')
```

```{r}
lm_plot_keyword(terrorism_data, 'recruitment', 'Trend for \'recruitment\' before and after June 2013')
```

## 3.3 Time-series Analysis

## 3.4 Trend Recovery

<!-- ```{r , echo=FALSE} -->

<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->


<!-- save(trend_data, file = "terrorism_May_11.RData") -->
<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = prediction)) + -->
<!--   geom_smooth(aes(ymin = LoCI, -->
<!--                   ymax = HiCI, -->
<!--                   color = surveillence), -->
<!--               stat = "identity") + -->
<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   scale_y_continuous(labels = comma) -->
<!-- ``` -->
<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = prediction)) + -->
<!--   geom_smooth(aes(ymin = LoCI, -->
<!--                   ymax = HiCI, -->
<!--                   color = surveillence), -->
<!--               stat = "identity") + -->
<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   scale_y_continuous(labels = comma) -->

<!-- ``` -->
<!-- ```{r , echo=FALSE} -->

<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2014-12-3'] <- 'after_after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = prediction)) + -->
<!--   geom_smooth(aes(ymin = LoCI, -->
<!--                   ymax = HiCI, -->
<!--                   color = surveillence), -->
<!--               stat = "identity") + -->
<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--    theme_bw(base_size = 5) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->



<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = views)) + -->
<!--   geom_smooth(aes(ymin = 0, -->
<!--                   ymax = 0, -->
<!--                   color = surveillence), -->
<!--               stat = "identity") + -->
<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   scale_y_continuous(labels = comma) -->

<!-- ``` -->



<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = views)) + -->

<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2014-12-31'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--    theme_bw(base_size = 5) + -->
<!--   scale_y_continuous(labels = comma) -->

<!-- ``` -->




<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->


<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->


<!-- #fit <- lm(views ~ month + I(month^2), data = monthly_agg) -->

<!-- #plot(views~month) -->
<!-- #points(month, fitted(fit), col='red', pch=20) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = views)) + geom_point()+stat_smooth(se=T)+ -->

<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->






<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->


<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->


<!-- #fit <- lm(views ~ month + I(month^2), data = monthly_agg) -->

<!-- #plot(views~month) -->
<!-- #points(month, fitted(fit), col='red', pch=20) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = views)) + geom_point()+stat_smooth(method="loess", se=F)+ -->

<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->




<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->


<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->


<!-- #fit <- lm(views ~ month + I(month^2), data = monthly_agg) -->

<!-- #plot(views~month) -->
<!-- #points(month, fitted(fit), col='red', pch=20) -->
<!-- monthly_agg$month <- as.numeric(monthly_agg$month) -->
<!-- fit <- lm(views~poly(month,5,raw=TRUE),monthly_agg) -->
<!-- plot(views~month,monthly_agg) -->
<!-- curve(predict(fit,newdata=data.frame(month=x)),add=T) -->
<!-- ``` -->





<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->


<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->


<!-- #fit <- lm(views ~ month + I(month^2), data = monthly_agg) -->

<!-- #plot(views~month) -->
<!-- #points(month, fitted(fit), col='red', pch=20) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = views)) + geom_point()+stat_smooth( se=T)+ -->

<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--   theme_bw(base_size = 5) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->



<!-- ```{r , echo=FALSE} -->


<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->


<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->




<!-- #fit <- lm(views ~ month + I(month^2), data = monthly_agg) -->

<!-- #plot(views~month) -->
<!-- #points(month, fitted(fit), col='red', pch=20) -->
<!-- monthly_agg$month <- as.numeric(monthly_agg$month) -->
<!-- fit <- lm(views~poly(month,5,raw=TRUE),monthly_agg) -->
<!-- plot(views~month,monthly_agg) -->
<!-- curve(predict(fit,newdata=data.frame(month=x)),add=T) -->
<!-- ``` -->



<!-- ```{r , echo=FALSE} -->

<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2014-12-3" -->
<!--   ) -->

<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- plot_before <- monthly_agg$views[monthly_agg$month < '2013-06-01'] -->
<!-- plot_after <- monthly_agg$views[monthly_agg$month >= '2013-06-01'] -->

<!-- plot_before <- sum(plot_before) -->
<!-- plot_after <- sum(plot_after) -->

<!-- df <- data.frame(Date1=c("After_June_2013", "Before_June_2013"), -->
<!--                 Total_Views=c(plot_after, plot_before)) -->
<!-- df$Date <- factor(df$Date1, c("Before_June_2013", "After_June_2013")) -->
<!-- ggplot(data=df, aes(x=Date, y=Total_Views, width=0.2)) + -->
<!--   scale_y_continuous(name="Total Views", labels = comma) + -->
<!--   theme_bw(base_size = 10) + -->
<!--   geom_bar(stat="identity") -->


<!-- ``` -->




<!-- ```{r , echo=FALSE} -->

<!-- terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear') -->

<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2015-12-31" -->
<!--   ) -->



<!-- trend_data <- -->
<!--   wp_trend( -->
<!--     page = terrorism_topics, -->
<!--     lang = "en", -->
<!--     from = "2011-12-01", -->
<!--     to   = "2019-04-10" -->
<!--   ) -->


<!-- #plot(trend_data) -->

<!-- #trend_data %>% -->
<!-- #  group_by(article, month=floor_date(date, "month")) %>% -->
<!-- #  summarize(views=sum(views)) %>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point(aes(color = article)) -->

<!-- monthly_agg <- trend_data %>% -->
<!--   group_by(month=floor_date(date, "month")) %>% -->
<!--   summarize(views=sum(views)) -->
<!-- #%>% -->
<!-- #  ggplot(aes(x = month, y = views)) + -->
<!-- #  geom_point() -->

<!-- monthly_agg$surveillence <- 'before' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2014-12-3'] <- 'after_after' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2016-06-3'] <- 'after_after_after' -->
<!-- monthly_agg$surveillence[monthly_agg$month >= '2016-06-3'] <- 'after_after_after_after' -->

<!-- model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg) -->
<!-- summary(model) -->

<!-- #plot(predict(model, monthly_agg)) -->

<!-- monthly_agg$prediction <- predict(model, monthly_agg) -->
<!-- monthly_agg$se <- predict(model, monthly_agg, -->
<!--                       se.fit = TRUE)$se.fit -->
<!-- z.val <- qnorm(1 - (1 - 0.90)/2) -->
<!-- monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se -->
<!-- monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se -->
<!-- #effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE) -->

<!-- monthly_agg$month <- ymd(monthly_agg$month) -->

<!-- ggplot(monthly_agg, -->
<!--        aes(x = month, -->
<!--            y = prediction)) + -->
<!--   geom_smooth(aes(ymin = LoCI, -->
<!--                   ymax = HiCI, -->
<!--                   color = surveillence), -->
<!--               stat = "identity") + -->
<!--   geom_point(data = monthly_agg, aes(x=month, y = views)) + -->
<!--   geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2016-06-3'), linetype = 2, colour = 'blue') + -->
<!--   geom_vline(xintercept = as.Date('2016-06-3'), linetype = 2, colour = 'blue') + -->
<!--   ylab('Views') + -->
<!--   xlab('Time (monthly)') + -->
<!--   scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) + -->
<!--    theme_bw(base_size = 5) + -->
<!--   scale_y_continuous(labels = comma) -->


<!-- ``` -->


The following is a list of all packages used to generate these results. (Leave at very end of file.)

```{r}
sessionInfo()
```