---
title: "MSD 2019 Final Project"
subtitle: "A replication and extension of < PAPER TITLE > by < ORIGINAL AUTHORS >, < PUBLISHED IN >"
author: "Your Names (your unis)"
date: '`r Sys.time()`'
output:
  pdf_document:
    toc: yes
    toc_depth: 3
---

1. Introduction

This Rmd file attempts to replicate and extend the results in CHILLING EFFECTS: ONLINE
SURVEILLANCE AND WIKIPEDIA USE by Jonathon W. Penney in Berkeley Technology Law Journal.
The author is a research fellow at University of Toronto. This single author paper has 
H5-index of 21. This paper is about the NSA/PRISM surveillance 2007, where United States
National Security Agency (NSA) started collecting Internet communications from various US
Internet companies. This information was made public in 2013 by Edward Snowden revelations.
This paper deals with the NSA paranoia where the paper studies traffic to Wikipedia articles 
on topics that raise privacy concerns for Wikipedia users before and after the Edward Snowden
revelations. The Wikipedia traffic was chosen because over 50% of Internet users use 
Wikipedia as a source of information. Over ⅓ of Americans annually access Wikipedia as a 
source of information and is in top 10 of most popular sites on the internet. 



```{r setup, include=FALSE}

library(here)
library(scales)
library(igraph)


library(tidyverse)
library(lubridate)
library(wikipediatrend)

theme_set(theme_bw())

knitr::opts_chunk$set(echo = TRUE)
```

```{r load data}
load("data/terrorism_data.RData")
load("data/infra_data.RData")
load("data/popular_data.RData")
load("data/terrorism_data_long.RData")
```

```{r example}
monthly_agg <- terrorism_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)
```




The following is a list of all packages used to generate these results. (Leave at very end of file.)

```{r}
sessionInfo()
```








```{r pressure, echo=FALSE}

terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )


save(trend_data, file = "terrorism_May_11.RData")
#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)
```
```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)

```
```{r pressure, echo=FALSE}

terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'
monthly_agg$surveillence[monthly_agg$month >= '2014-12-3'] <- 'after_after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
   theme_bw(base_size = 5) +
  scale_y_continuous(labels = comma)


```



```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = views)) +
  geom_smooth(aes(ymin = 0, 
                  ymax = 0,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)

```



```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = views)) +
 
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2014-12-31'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
   theme_bw(base_size = 5) +
  scale_y_continuous(labels = comma)

```




```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)


#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)


#fit <- lm(views ~ month + I(month^2), data = monthly_agg)

#plot(views~month)
#points(month, fitted(fit), col='red', pch=20)

ggplot(monthly_agg,
       aes(x = month,
           y = views)) + geom_point()+stat_smooth(se=T)+
 
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)


```






```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)


#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)


#fit <- lm(views ~ month + I(month^2), data = monthly_agg)

#plot(views~month)
#points(month, fitted(fit), col='red', pch=20)

ggplot(monthly_agg,
       aes(x = month,
           y = views)) + geom_point()+stat_smooth(method="loess", se=F)+
 
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2015-12-31'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  scale_y_continuous(labels = comma)


```




```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)


#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)


#fit <- lm(views ~ month + I(month^2), data = monthly_agg)

#plot(views~month)
#points(month, fitted(fit), col='red', pch=20)
monthly_agg$month <- as.numeric(monthly_agg$month)
fit <- lm(views~poly(month,5,raw=TRUE),monthly_agg)
plot(views~month,monthly_agg)
curve(predict(fit,newdata=data.frame(month=x)),add=T)
```





```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)


#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)


#fit <- lm(views ~ month + I(month^2), data = monthly_agg)

#plot(views~month)
#points(month, fitted(fit), col='red', pch=20)

ggplot(monthly_agg,
       aes(x = month,
           y = views)) + geom_point()+stat_smooth( se=T)+
 
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
  theme_bw(base_size = 5) +
  scale_y_continuous(labels = comma)


```



```{r pressure, echo=FALSE}


terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)


#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)




#fit <- lm(views ~ month + I(month^2), data = monthly_agg)

#plot(views~month)
#points(month, fitted(fit), col='red', pch=20)
monthly_agg$month <- as.numeric(monthly_agg$month)
fit <- lm(views~poly(month,5,raw=TRUE),monthly_agg)
plot(views~month,monthly_agg)
curve(predict(fit,newdata=data.frame(month=x)),add=T)
```



```{r pressure, echo=FALSE}

terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2014-12-3"
  )

#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

plot_before <- monthly_agg$views[monthly_agg$month < '2013-06-01'] 
plot_after <- monthly_agg$views[monthly_agg$month >= '2013-06-01'] 

plot_before <- sum(plot_before)
plot_after <- sum(plot_after)

df <- data.frame(Date1=c("After_June_2013", "Before_June_2013"),
                Total_Views=c(plot_after, plot_before))
df$Date <- factor(df$Date1, c("Before_June_2013", "After_June_2013"))
ggplot(data=df, aes(x=Date, y=Total_Views, width=0.2)) +
  scale_y_continuous(name="Total Views", labels = comma) +
  theme_bw(base_size = 10) +
  geom_bar(stat="identity")


```




```{r pressure, echo=FALSE}

terrorism_topics <- c('Al-Qaeda', 'Terrorism', 'Terror', 'Environmental_terrorism', 'Eco-terrorism', 'Conventional_weapon', 'Weapons-grade', 'Dirty_bomb', 'Nuclear_enrichment', 'nuclear')

trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2015-12-31"
  )



trend_data <- 
  wp_trend(
    page = terrorism_topics, 
    lang = "en", 
    from = "2011-12-01",
    to   = "2019-04-10"
  )


#plot(trend_data)

#trend_data %>% 
#  group_by(article, month=floor_date(date, "month")) %>%
#  summarize(views=sum(views)) %>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point(aes(color = article))

monthly_agg <- trend_data %>% 
  group_by(month=floor_date(date, "month")) %>%
  summarize(views=sum(views)) 
#%>%
#  ggplot(aes(x = month, y = views)) +
#  geom_point()

monthly_agg$surveillence <- 'before'
monthly_agg$surveillence[monthly_agg$month >= '2013-06-01'] <- 'after'
monthly_agg$surveillence[monthly_agg$month >= '2014-12-3'] <- 'after_after'
monthly_agg$surveillence[monthly_agg$month >= '2016-06-3'] <- 'after_after_after'
monthly_agg$surveillence[monthly_agg$month >= '2016-06-3'] <- 'after_after_after_after'

model <- lm(views ~ month + surveillence + month*surveillence, data = monthly_agg)
summary(model)

#plot(predict(model, monthly_agg))

monthly_agg$prediction <- predict(model, monthly_agg)
monthly_agg$se <- predict(model, monthly_agg,
                      se.fit = TRUE)$se.fit
z.val <- qnorm(1 - (1 - 0.90)/2)
monthly_agg$LoCI <- monthly_agg$prediction - z.val * monthly_agg$se
monthly_agg$HiCI <- monthly_agg$prediction + z.val * monthly_agg$se
#effect_plot(model, pred = view, interval = TRUE, plot.points = TRUE)

monthly_agg$month <- ymd(monthly_agg$month)

ggplot(monthly_agg,
       aes(x = month,
           y = prediction)) +
  geom_smooth(aes(ymin = LoCI, 
                  ymax = HiCI,
                  color = surveillence),
              stat = "identity") +
  geom_point(data = monthly_agg, aes(x=month, y = views)) +
  geom_vline(xintercept = as.Date('2013-06-01'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2014-12-3'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2016-06-3'), linetype = 2, colour = 'blue') +
  geom_vline(xintercept = as.Date('2016-06-3'), linetype = 2, colour = 'blue') +
  ylab('Views') +
  xlab('Time (monthly)') +
  scale_x_date(date_breaks = "6 month", labels = date_format("%Y-%b")) +
   theme_bw(base_size = 5) +
  scale_y_continuous(labels = comma)


```